---
title: "The User's Manual of RXAJ"
author: "CHEN Longzan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r}
  load("E:\\RXAJ\\RXAJ\\.RData")
```

  RXAJ is a hydrology model package which coded by R script and C language. This package is used for simluating and precasting the outlet discharage of basin(watershed,catchment), with the history discharge data, rainfall data and the sub-basin data. RXAJ has provided the following features:

# Data Management Module
## Data Structure figure
<img src="E:\\oneDrive\\workOnHand\\RXAJ\\数据结构.bmp" />

## modelParameter(dataframe)
the modelParameter includes the day-model and flood-model parameter, showing as the following :

```{r}
knitr::kable(modelPapameter)
```

## basinInfo(list)
the basinInfo includes the sub-basin information and the basin area (km2),
### sub-baisn(dataframe)
the sub-basin information, which including the sub-basin area-weight and river-reach-number, was showing as the following :

```{r}
knitr::kable(basinInfo[[1]])
```

### basin area(numeric)
the baisn area is the whole basin area, which unit is square kilometers.

## dayData(list)
the dayData includes dayStart,dayEnd,dayE,dayP,dayQ,initValue, which needed by the day model.
### dayStart and dayEnd
the dayStart is the start time of the day-model while the dayEnd means the end time of the day-model.A simple example is "2018-01-01".
### dayE(dataframe)
the dayE includes the whole basin evapotranspiration value and the  corresponding date.Showing as the following:

```{r}
knitr::kable(head(dayE,6))
```

### dayP(dataframe)
the dayP includes the sujb-baisn preciptation value and the corresponding date.Showing as the following:

```{r}
knitr::kable(head(dayP,6))
```

### dayQ(dataframe)
the dayQ includes the measured outlet discharge value and the corresponding date.Showing as the following:

```{r}
knitr::kable(head(dayQ,6))
```

### initValue(dataframe)
the initValue includes the initial condition of day-model, showing as the following:

```{r}
knitr::kable(initialValue)
```

## floodData(list)
the floodData is nearly similar as the dayData, including timeStart,timeEnd,hourE,hourP,hourQ,initValue.

### hourStart and hourEnd
the hourStart is the start time of the flood-model while the hourEnd means the end time of the flood-model.A simple example is "2018-01-01 08:00:00".

### hourE
the hourE includes the whole basin evapotranspiration value and the  corresponding date.Showing as the following:

```{r}
knitr::kable(head(floodData1$hourE,6))
```

### hourP
the hourP includes the sujb-baisn preciptation value and the corresponding date.Showing as the following:

```{r}
knitr::kable(head(floodData1$hourP,6))
```

### hourQ
the hourQ includes the measured and calculated outlet discharge value and the corresponding date, you may keep the calculated value be 0.0 first. Showing as the following:

```{r}
knitr::kable(head(floodData1$hourQ,6))
```

### initValue
the initValue includes the initial condition of hour-model, showing as the following:

```{r}
knitr::kable(initialValue)
```

# Function Introduction

## check_basinData(basinData)

### Parameter
- basinData: the integrated basinData(list)

### feature
this function may help you check the integrity of your basinData, including the following checking item:
- whether the discharge data, preciptation data and the evapotraspiration data are corresponded to the start and end date.
- whether the discharge data, preciptation data and the evapotraspiration data are sequential.
- whether the discharge data, preciptation data and the evapotraspiration data have NA.
- whether the number of sub-basin is consistent in everywhere.

## dXAJ(dayModelParameter,basinInfo,dayData)

### Parameter
- dayModelParamter: the day-model parameter.
- basinInfo: the basin information including the sub-basin area-weight value ,the number of sub-river-reach and the area of the basin.
- dayData: the day data list of the basin.

### Feature
this function is used to simluate the day discharge of the basin, which output may including the following:
- dayResult: the dayResult is used for initializing the flood-model.
- resultData: the resultData includes the preciptation data, calculated discharge data, measured discharge data and the corresponding date, showing as the following:

```{r}
knitr::kable(head(resultData,6))
```

## initHourData(dayStart,floodData)

### Parameter
- dayStart: the start date of the flood.
- floodData: the integrated flood data.

### Feature
this function is used for providing the initValue of flood-model from the day-model output(dayResult). The return output is floodData.


## hXAJ(hourModelParameter,basinInfo,floodData)

### Parameter
- hourModelParameter: the flood-model parameter.
- basinInfo: the basin information, same as the dXAJ.
- floodData: the hour data list of the basin.

### Feature
this function is used to simluate the flood discharge of the basin, which output may including the following:
- floodResult: the floodResult inculdes the preciptation data, calculated discharge data, measured discharge data and the corresponding date, showing as the following:

## changeModelParameter(parameterValue,paraIndex,value)

### Parameter
- parameterValue: the numeric vector of the parameter, which is correspended with the parameter name vector,parameterName<-c("KC","UM","LM","C","WM","B","IM","SM","EX","KG","KI","CI","CG","CS","L","KE","XE").
- paraIndex: the parameter name(string) which will be modified.
- value: the parameter new value(numeric) .

### Feature
this function is used for change the paramter value of day-model or flood-model. The return variable is parameterValue.

## showResult(Date,P,Qcal,Qmea)

### Parameter
- Date:the Date series.
- P: the preciptation series.
- Qcal: the calculated discharge series.
- Qmea: the measured discharge series.

### Feature
this function is used for show the simluation result with package recharts.